### 2015-02-05 ms/ms.Rmd
Change link
Fix links, reword ambiguous text, fix license

Until recently, most scientific publications in biology have mostly been concerned with "small data" `r citep("10.1038/nj7461-243a")`. Datasets arrive in small parcels, corresponding to the work of an individual study, or perhaps a handful of studies. It is exciting to be able to put these parcels together, to create something larger. We hope others will use this dataset and build on it. See [https://github.com/dfalster/baad](https://github.com/dfalster/baad) for information on how to contribute to future releases.

@@

**Latest update**: The dataset made available through this publication was processed on 2014-12-15. Newer updates may be retrieved from the BAAD website ([https://github.com/dfalster/baad/](https://github.com/dfalster/baad/).

@@

**1. Storage location and medium**: The data published here is the first release from the Biomass and allometry database stored at [https://github.com/dfalster/baad/](https://github.com/dfalster/baad/). The version of the data made available for this publication is available here ((LINK TO ECOLOGICAL ARCHIVES DATA FILE)). For scientific analyses, we suggest you use this version.

Development versions of the dataset will continue to be available at [https://github.com/dfalster/baad/](https://github.com/dfalster/baad/).

If you notice any problems with the dataset, please list an issue [here](https://github.com/dfalster/baad/issues/new).

@@

**Copyright restrictions**: The dataset is released under the [Creative Commons CC0 license](http://creativecommons.org/choose/zero/?lang=en). As such, it may be freely used and redistributed. When using the dataset, we kindly request that you cite this article, recognizing the hard work that went into collecting the data and the authors' willingness to make it publicly available.

>>>>

Until recently, most scientific publications in biology have mostly been concerned with "small data" `r citep("10.1038/nj7461-243a")`. Datasets arrive in small parcels, corresponding to the work of an individual study, or perhaps a handful of studies. It is exciting to be able to put these parcels together, to create something larger. We hope others will use this dataset and build on it. See [github.com/dfalster/baad](https://github.com/dfalster/baad) for information on how to contribute to future releases.

@@

**Latest update**: The dataset made available through this publication was processed on 2014-12-15. Newer updates may be retrieved from the BAAD website [github.com/dfalster/baad](https://github.com/dfalster/baad).

@@

**1. Storage location and medium**: The data published on Ecological Archives is the first release from the Biomass and allometry database (v1.0.0) stored at [github.com/dfalster/baad](https://github.com/dfalster/baad/). The version of the data contained in this publication can also be downloaded from the releases page on gihtub: [github.com/dfalster/baad/releases](https://github.com/dfalster/baad/releases). Development versions of the dataset will continue to be made available at [github.com/dfalster/baad](https://github.com/dfalster/baad).

If you notice any problems with the dataset, please list an issue at [github.com/dfalster/baad/issues/new](https://github.com/dfalster/baad/issues/new).

@@

**Copyright restrictions**: The dataset is released under the the [Creative Commons Zero](https://creativecommons.org/publicdomain/zero/1.0/) public domain dedication. When using the dataset, we kindly request that you cite this article, recognizing the hard work that went into collecting the data and the authors' willingness to make it publicly available.
